### 2013-06-12 paper_draft.tex
fixed linebreaks
well, made the F for figure uppercase so they might find it.

In the same timeframe mentioned above, all users combined have 
entered a total of 4743 variations on 130 different phenotypes with those variations being 
the different values on a given trait or phenotype. The mean number of users that have entered their variations for a single phenotype 
is 36.48. The distribution of how many users have 
entered their data per phenotype, compared to the amount of unique phenotypes, can be seen in figure \ref{pheno}. The phenotype provided by the most users is "eye color", for which 207 users entered their phenotype (retrieved 10/27/2012).

@@

\section*{Figure Legends}
\begin{figure}[!ht]
	\begin{center}
		\includegraphics[scale=0.35]{25_10_2012_Graphs/users.png}
	\end{center}
	\caption{
	{\bf Growth of openSNP-user-accounts.} The increase in numbers for users from 27.09.2011 to 27.10.2012 is shown.} 
	\label{Figure1_label}
\end{figure}
\begin{figure}[!ht]
	\begin{center}
		\includegraphics[scale=0.35]{25_10_2012_Graphs/genotypes.png}
	\end{center}
	\caption{
	{\bf Growth of available genotypings.} The increase in numbers for genotyping-files from 27.09.2011 to 27.10.2012 is shown.} 
	\label{Figure2_label}
\end{figure}
\begin{figure}[!ht]
	\begin{center}
		\includegraphics[scale=0.40]{25_10_2012_Graphs/phenotypes_vs_userphenotypes.png}
	\end{center}
	\caption{
	{\bf Development of unique phenotypes and phenotypic information over time.} The x-axis shows the time-frame from start of the project until October 2012, the left y-axis shows how many unique phenotypes have been entered, and the right y-axis shows the amount of phenotypes users entered.}
	\label{pheno}
\end{figure}

\begin{figure}[!ht]
	\begin{center}
		\includegraphics[scale=0.5]{25_10_2012_Graphs/papers_dotchart.png}
	\end{center}
	\caption{
	{\bf Distribution of annotation-sources at openSNP.} Currently, SNP-annotations from SNPedia, PLOS, Mendeley, the \emph{GET Evidence System} and the \emph{NHGRI GWAS Catalog} are being collected.}
	\label{Figure3_label}
\end{figure}

\begin{figure}[!ht]
	\begin{center}
		\includegraphics[scale=0.6]{25_10_2012_Graphs/new_pie.png}
	\end{center}
	\caption{
	{\bf Ratio of open access Publications.} Green pieces are open access. The \emph{NHGRI GWAS Catalog} doesn't give information about the open access status.}
	\label{oa_label}
\end{figure}

\begin{figure}[!ht]
	\begin{center}
	  \includegraphics[scale=0.3]{latest_uml.png}
	\end{center}
	\caption{
	{\bf Flow of data inside openSNP.} External databases and user-provided data are used as input. Output of data is done using the website, the \emph{Distributed Annotation System} and a JSON-API.} 
	\label{Figure4_label}
\end{figure}

>>>>

In the same timeframe mentioned above, all users combined have 
entered a total of 4743 variations on 130 different phenotypes with those variations being 
the different values on a given trait or phenotype. The mean number of users that have entered their variations for a single phenotype 
is 36.48. The distribution of how many users have 
entered their data per phenotype, compared to the amount of unique phenotypes, can be seen in Figure \ref{pheno}. The phenotype provided by the most users is "eye color", for which 207 users entered their phenotype (retrieved 10/27/2012).

@@

\section*{Figure Legends}
\begin{figure}[!ht]
	%\begin{center}
	%	\includegraphics[scale=0.35]{25_10_2012_Graphs/users.png}
	%\end{center}
	\caption{
	{\bf Growth of openSNP-user-accounts.} The increase in numbers for users from 27.09.2011 to 27.10.2012 is shown.} 
	\label{Figure1_label}
\end{figure}
\begin{figure}[!ht]
	%\begin{center}
	%	\includegraphics[scale=0.35]{25_10_2012_Graphs/genotypes.png}
	%\end{center}
	\caption{
	{\bf Growth of available genotypings.} The increase in numbers for genotyping-files from 27.09.2011 to 27.10.2012 is shown.} 
	\label{Figure2_label}
\end{figure}
\begin{figure}[!ht]
	%\begin{center}
	%	\includegraphics[scale=0.40]{25_10_2012_Graphs/phenotypes_vs_userphenotypes.png}
	%\end{center}
	\caption{
	{\bf Development of unique phenotypes and phenotypic information over time.} The x-axis shows the time-frame from start of the project until October 2012, the left y-axis shows how many unique phenotypes have been entered, and the right y-axis shows the amount of phenotypes users entered.}
	\label{pheno}
\end{figure}

\begin{figure}[!ht]
	%\begin{center}
	%	\includegraphics[scale=0.5]{25_10_2012_Graphs/papers_dotchart.png}
	%\end{center}
	\caption{
	{\bf Distribution of annotation-sources at openSNP.} Currently, SNP-annotations from SNPedia, PLOS, Mendeley, the \emph{GET Evidence System} and the \emph{NHGRI GWAS Catalog} are being collected.}
	\label{Figure3_label}
\end{figure}

\begin{figure}[!ht]
	%\begin{center}
	%	\includegraphics[scale=0.6]{25_10_2012_Graphs/new_pie.png}
	%\end{center}
	\caption{
	{\bf Ratio of open access Publications.} Green pieces are open access. The \emph{NHGRI GWAS Catalog} doesn't give information about the open access status.}
	\label{oa_label}
\end{figure}

\begin{figure}[!ht]
	%\begin{center}
	%  \includegraphics[scale=0.3]{latest_uml.png}
	%\end{center}
	\caption{
	{\bf Flow of data inside openSNP.} External databases and user-provided data are used as input. Output of data is done using the website, the \emph{Distributed Annotation System} and a JSON-API.} 
	\label{Figure4_label}
\end{figure}
